---
title: "WUp-Linear-Model-with-prediction-2"
author: "Maximiliano Ortiz"
date: "2025-10-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tigerstats)
require(knitr)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```

###Model1: Sims-ARM

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```

```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARM") +theme (plot.title = element_text(hjust = 0.5, size = 20))

```


###Numerical Results

```{r}
cor(SIMS~ARM,data=data)
```

###Inferintal Results

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

### Create target

```{r}
target <- data.frame(ARM=90,GRIP=90)
```

### Predict Target Point of Model 1

```{r}
predict(model.1,target,interval =c("prediction"))
```


### Linear Fit Model1

```{r}
basicNN + geom_point () + ggtitle("SIMS-ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20)) + geom_smooth(method = lm)
```


##Model2: Sims~GRIP
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))
```

```{r}
basicNN + geom_point() +ggtitle("SIMS vs GRIP")+ theme(plot.title = element_text(hjust=0.5,size=20))
```


###Numerical Results

```{r}
cor(SIMS~GRIP,data=data)
```

###Inferintal Results

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```


### Predict Target Point of Model 2

```{r}
predict(model.2,target,interval =c("prediction"))
```


### Linear Fit Model2

```{r}
basicNN + geom_point () + ggtitle("SIMS-GRIP") + theme(plot.title = element_text(hjust = 0.5, size = 20)) + geom_smooth(method = lm)
```


##Model3: Sims~ARM+GRIP




###Numerical Results Model 3 

```{r}
cor(SIMS~ARM+GRIP,data=data)
```

The correlation number for model 3 (SIM~ARM+GRIP) is higher compared to model 2 (SIM~GRIP) and model 1 (SIM~ARM), so the correlation is better using both (ARM+GRIP) models than just 1 (either ARM or GRIP).


###Inferintal Results Model 3 

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```

The formula for getting model 3 is SIMS= -5.433871 +  0.037311*ARM + 0.024470*GRIP 

### Predict Target Point of Model 3

```{r}
predict(model.1,target,interval =c("prediction"))
```

```{r}
predict(model.2,target,interval =c("prediction"))
```

```{r}
predict(model.3,target,interval =c("prediction"))
```


### Anova Test for Models 



###Model1~Model3

```{r}
anova(model.1,model.3) 
```

Our P-value was 0.000004994 which is very small. Which tells us that model 3 is better than model 1 in a significant difference. 


###Model2~Model3

```{r}
anova(model.2,model.3) 
```

Our P-value for model 2 and 3 (0.000000001495) is smaller than model 1 and 3 (0.000004994). Which tells us that model 3 is the most accurate model out of the 3. 

###Model1~Model2

```{r}
anova(model.1,model.2) 
```

The sum of Residual sum of square errors of model 2 is greater than model 1. The difference of the two models is -25.189. 

### Conclusion and Disscusion 

IN this assignment I learned to import the data from a given website. I was able to manipulate the data into 3 models. The first model was SIMS~ARM, the second was SIMS~GRIP, and the third was SIMS~ARM+GRIP. I used a prediction code to estimate the values along the scatter plots to visualiesthe lines of best fit. I then used anova to compare all 3 models, which showed that model 3 had the best accurate. 


